Assessment of simulation procedures and robust methods for Mendelian randomization analysis

### 2022-11-10 presentation/robustMR.qmd
added references

---
title: "Assessment of simulation procedures and robust methods for Mendelian randomization analysis"
author: "Christoph Reich"
date: "`r Sys.Date()`"
title-slide-attributes: 
  data-background-image: ../templates/bg1.png
  data-background-size: cover  # default
  data-background-opacity: "1"  # from 0-1
format: 
  revealjs:
    slide-number: true
    scrollable: true
    navigation-mode: vertical
    chalkboard:   # kreidetafel
      theme: whiteboard
      boardmarker-width: 5
      buttons: false
    incremental: false  # display bullet lists all at once
    preview-links: auto
    logo: ../templates/mederlab_logo.png
    css: ../templates/main.css
    footer: "robustMRmethods"
    theme: [simple, ../templates/custom.scss]
    #self-contained: true  # for distribution (slows rendering), not compatible with chulkboarddic
# reference-doc: templates/20210129_mederslidemaster.pptx  # only for pptx rendering
bibliography: ../references/references.bib
---

@@

* The variance in BMI explained by the IVs is calculated with the following formula: $explained\ variance = 2f(1-f)\beta^2$, where $f$ denotes the allele frequency and $\beta$ is the additive genetic effect. 
* The explained variance in liability to GSD and GBC is calculated as described by @So_2011.

@@

##  {background-image="../templates/bg4.png"}

@@

>>>>

---
title: "Assessment of simulation procedures and robust methods for Mendelian randomization analysis"
author: "Christoph Reich"
date: "`r Sys.Date()`"
title-slide-attributes: 
  data-background-image: ../templates/bg1.png
  data-background-size: cover  # default
  data-background-opacity: "1"  # from 0-1
format: 
  revealjs:
    slide-number: true
    scrollable: true
    navigation-mode: vertical
    #chalkboard:   # kreidetafel
    #  theme: whiteboard
    #  boardmarker-width: 5
    #  buttons: false
    incremental: false  # display bullet lists all at once
    preview-links: auto
    logo: ../templates/mederlab_logo.png
    css: ../templates/main.css
    footer: "robustMRmethods"
    theme: [simple, ../templates/custom.scss]
    self-contained: true  # for distribution (slows rendering), not compatible with chulkboarddic
# reference-doc: templates/20210129_mederslidemaster.pptx  # only for pptx rendering
bibliography: ../references/references.bib
---

@@

* The variance in BMI explained by the IVs is calculated with the following formula: $explained\ variance = 2f(1-f)\beta^2$, where $f$ denotes the allele frequency and $\beta$ is the additive genetic effect. 
* The explained variance in liability to GSD and GBC is calculated as described by @So_2011
  + Prevalence of disease $K$ must be set:
      - [Prevalence GSD](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3343155/#:~:text=Gallstones%20are%20common.,develop%20stones%20at%20some%20time.&text=The%20majority%20will%20not%20develop,cholecystitis,%20cholangitis,%20or%20pancreatitis)
      - [Prevalence GBC](https://www.wcrf.org/cancer-trends/gallbladder-cancer-statistics/)

@@

---
##  {background-image="../templates/bg4.png"}

@@

:::
---
